Hydra Battles and Cie

### 2021-01-14 doc/hydras.tex
minor modifications
add a new chapter on primitive recursive functions

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex
\begin{document}
\maketitle

@@

@@

\include{part-hydras}

\part{Some Funny Algorithms}

@@

\chapter*{Index and tables}

>>>>

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury\\ \emph{The formalization of primitive recursive functions was originally authored by Russel O'Connor}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex
\begin{document}
\maketitle

@@

The formalization of primitive recursive functions was originally a part of  Russel O'Connor's work on G\"odel's incompleteness theorems~\cite{OConnor05}.

@@

\include{part-hydras}
\include{chapter-primrec}
\part{Some Funny Algorithms}

@@

\chapter{Index and tables}
